master thesis

### 2018-02-05 Paper - Latex/Paper - Skizze - v2.tex
Methods - add Workflow, Countings

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Methods}
  \anmerkung{Graphischen Workflow hinzufügen, mehr Motivation und genauer. (Bernhard)}

@@

    %---------------------------------------------------------------------------------------------------
    \subsection{Countings}
      Some simple countings...\\
      nr of parasites, free-living and unknown nodes ... from whole tree, subtrees...
      \begin{center}
        \begin{tabular}{ | l | p{3cm} | }
          \hline
          Name & Number of \\
          \hline \hline
          interactions & 5346414 \\ \hline
          freeliving species & 51337 (distinct) \\ \hline
          parasite species &  47332 (distinct) \\ \hline
          unused possible species & 57352 (source), 809993 (target) \\
          % number of freelivings: 489179
          % number of freelivings: 42657 (distinct)
          % number of parasites: 3353580
          % number of parasites: 44260 (distinct)
          % number of SAME_AS: 86198
          % number of SAME_AS: 16710 (distinct)
          \hline  
        \end{tabular}
      \end{center}

>>>>

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Methods}
  \anmerkung{Graphischen Workflow hinzufügen, mehr Motivation und genauer. (Bernhard)}
  \begin{figure}[h!]
    \caption{Workflow}
    \centering
    \label{fig:Workflow}
    \includegraphics[width=1\textwidth]{Figures/Workflow.png}
  \end{figure}

@@

    %---------------------------------------------------------------------------------------------------
    \subsection{Countings}
      Some simple countings...\\
      nr of parasites, free-living and unknown nodes ... from whole tree, subtrees...
      \begin{center}
        \begin{tabular}{ | l | p{3cm} | }
          \hline
          Name & Number of \\
          \hline \hline
          interactions & 5346414 \\ \hline
          freeliving species & 51337 (distinct) \\ \hline
          parasite species &  47332 (distinct) \\ \hline
          unused possible species & 57352 (source), 809993 (target) \\ \hline
          % number of freelivings: 489179
          % number of freelivings: 42657 (distinct)
          % number of parasites: 3353580
          % number of parasites: 44260 (distinct)
          % number of SAME_AS: 86198
          % number of SAME_AS: 16710 (distinct)
          Eukaryota & 241974 internal nodes, 2293463 leaf nodes \\
          Chloroplastida has 43486 internal nodes and 412434 leaf_nodes
          % Metazoa has 179944 internal nodes and 1491012 leaf_nodes
          % Nematoda has 3437 internal nodes and 30127 leaf_nodes
          % Vertebrata has 30466 internal nodes and 88415 leaf_nodes
          % Tetrapoda has 21870 internal nodes and 47540 leaf_nodes
          % Mammalia has 4727 internal nodes and 8615 leaf_nodes
          % Primates has 492 internal nodes and 686 leaf_nodes
          % Hominidae has 12 internal nodes and 14 leaf_nodes
          % Fungi has 9534 internal nodes and 314571 leaf_nodes
          \hline  
        \end{tabular}
      \end{center}
      $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ -> only 4.3\% of leaf nodes are filled with information
